Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-12-13 Manuscript Analyses/manuscript_analysis.Rmd
rerendered analysis report

All data processing and analyses were conducted using R Version 4.4.1

@@

## Younger adult df
young_adult <- rio::import("cleaned_scored.csv") |>
  dplyr::select(-group_number)

@@

A total of 59 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.

@@

### Comparing Younger vs. Older Adults

#### Age-Corrected

The younger adult data comes from https://osf.io/y32qc/

older_adult <- pl_int |>
  dplyr::filter(type == "pretest") |>
  dplyr::select(id, ends_with("_c"), ends_with("_u"), best_win) |>
  dplyr::select(-c(fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u)) |>
  dplyr::rename(win = best_win) |>
  dplyr::mutate(group = "old") |>
  dplyr::filter()

young_adult <- young_adult |>
  dplyr::select(-c(age_in_years, win_l, win_r, fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u))

compare_df <- rbind(older_adult, young_adult)

compare_table_c <- compare_df %>%
  dplyr::select(id, ends_with("_c"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

compare_table_c

#### Uncorrected Scores

compare_table_u <- compare_df %>%
  dplyr::select(id, ends_with("_u"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_u,
    `Inhibitory Control` = flanker_u,
    `Cognitive Flexibility` = card_sort_u,
    `Receptive Vocabulary` = vocab_u,
    `Processing Speed` = pattern_u,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

compare_table_u

@@

Pretest and posttest intelligibility, as measured by percent words correct, for each of the two speaker conditions are presented below. On average, pretest intelligibility for AM1 was lower than PDM10. However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10. A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p \< .001, d = 1.01).

>>>>

All data processing and analyses were conducted using R Version 4.3.2.

@@

@@

A total of 58 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.

@@

@@

Pretest and posttest intelligibility, as measured by percent words correct, for each of the two speaker conditions are presented below. On average, pretest intelligibility for AM1 was lower than PDM10. However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10. A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,31) = 101.83, p \< .001, d = 1.05).
